### 2019-10-13 main_text/main_text.tex
Edits to model section & results/discussion

\paragraph*{Xanthosine dynamics.}
We have now discussed how xanthosine activates the synthesis of XapA and
XapB through XapR. In this part of the section, we close the feedback loop
by setting up a xanthosine rate equation.

Transport of xanthosine across the cell membrane happens in two steps which
we will discuss now. All statements in this paragraph are based on data
from~\cite{Norholm2001}. In a first transport step, xanthosine passes the
outer membrane through porins like Tsx, OmpF and OmpC. This does not seem to
be a rate-limiting step. Then, XapB actively transports it across the inner
membrane, powered by the proton motive force. There are two other active
nucleoside transporters that seem to be transporting xanthosine with a very
low affinity: NupC and NupG. It was found that \textDelta\emph{nupC}
\textDelta\emph{nupG} strains cannot grow on xanthosine. Hence, these seem
to be necessary to ``start'' the system by importing small amounts of
xanthosine that then activate \emph{xapB}, and there appears to be no other
significant way in which xanthosine can enter the cell.

@@

After transport into the cell, XapA degrades xanthosine. We model this using
standard Michaelis-Menten kinetics, with parameters $k_{\n{a}}, K_{\n{a}}$
(corresponding to turnover rate and Michaelis constant, respectively). All
the above then leads to the xanthosine rate equation
\begin{eqnarray}
\dd{\n{[x]}}{t} = \biggl(\underbrace{k_{\n{b,i}} \frac{c}{K_{\n{b,i}} + c} - k_{\n{b,e}} \frac{\n{[x]}}{K_{\n{b,e}} + \n{[x]}}}_{\n{XapB}} - \underbrace{k_{\n{a}} \frac{\n{[x]}}{K_{\n{a}} + \n{[x]}}}_{\n{XapA}}\biggr) \n{[p]} + \underbrace{k_{\n{nup}} \left(c- \xi \n{[x]}\right)}_{\n{NupC\ \& \ NupG}}.
\end{eqnarray}
We recall that $\n{[x]}$ is the intracellular xanthosine concentration, and
$c$ denotes the extracellular one. Because $k_{\n{b,i}} > k_{\n{b,e}}$ and
$K_{\n{b,i}} < K_{\n{b,e}}$, influx dominates at low intracellular
xanthosine concentrations. At much higher intra- than extracellular
xanthosine concentrations, the efflux term takes over. More details on the
aforementioned steps and a discussion of passive diffusion can be found
in~\nameref{S1_Text}.

@@

Very little is known about the \emph{xap} system, and thus, there are no
measured values for the free parameters. Nevertheless, we were able to
estimate a reasonable range by using values from similar, well studied
systems and by finding physical constraints or relations between parameters.
The results of these estimates are shown in Table~\ref{table1:nondim}. They
are based on a choice of $\gamma_{\n{p}} = 5 \cdot 10^{-4} \unit{s^{-1}}$
and $K_{\n{a}} = 5 \cdot 10^{-5} \unit{M}$. A detailed derivation can be
found in~\nameref{S1_Text}.

@@

\subsection*{Deterministic phase portraits}
A standard way to analyze dynamical systems like ours deterministically is
to plot phase portraits. In the following, we present such plots where the
state variables are the mRNA, the protein, and the xanthosine concentration.

\paragraph*{From a 3D to a 2D system.} 
Fig~\subref{fig4:bistability}{A} shows the 3D phase portrait for a
representative set of parameters (that from Table~\ref{table1:nondim}),
whose choice is explained below. The plot looks rather complicated at first
but can be understood intuitively. The three planes are the nullclines and
the gray lines point in the direction in which the dynamical system moves at
each point. The planes intersect in three points, which are the steady-state
solutions of the dynamical system. For this choice of parameters, the system
first flows towards the mRNA nullcline, then it moves along that plane to
the intersection with the protein nullcline, and lastly, it moves along that
intersection line to one of the three intersection points of all three
planes.

@@

It is important to point out that for a different set of parameters, the
dynamics can be quite different. There are, for example, scenarios where the
xanthosine kinetics are roughly as fast as the mRNA kinetics and the
dynamics unfolds in two steps: first to the intersection of the mRNA and the
xanthosine nullcline, then along that line to the protein nullcline and
thereby to a fixed point.

A usual simplification with genetic circuits like this is to assume the mRNA
concentration to be at steady-state, i.e. to write $\dd{\n{[m]_a}}{\tau}=0$
and solve this for $\n{[m]_a}(\n{[p]_a},\n{[x]_a})$ to simplify the 3D to a
2D system. This restricts the dynamics to the green plane in our plot, which
is reasonable here because as explained above, the system first flows
towards that plane before either the protein or the xanthosine concentration
changes significantly. However, as already pointed out, this is different
for other parameter values, and thus, this assumption generally is not a
good one. If the xanthosine dynamics are faster than the mRNA dynamics, the
system first flows towards the xanthosine nullcline. In that case, forcing
it onto the mRNA nullcline leads to significant changes in the dynamics.

@@

\paragraph*{Bistability.} 
From the 2D plot in Fig~\subref{fig4:bistability}{B}, it can clearly be seen
that for the chosen parameters, there are three steady-state solutions.
Because the 2D plane that we are in now is the mRNA nullcline, these
solutions are the same fixed points as in the 3D plot
($\dd{\n{[m]_a}}{\tau}=0$ on the nullcline and $\dd{\n{[p]_a}}{\tau}=0$,
$\dd{\n{[x]_a}}{\tau}=0$ for the 2D fixed points). One can see from the
vector field that the two outer points (labeled 1 and 3) are stable and the
middle one (labeled 2) is unstable and serves as a sort of ``switch-point''
between the other two. This means that there are two stable states the cell
can be in, one at high (point 3) and one at low (point 1) expression. As a
result, there is bistability and the distribution of expression among cells
is bimodal.

This corresponds to the experimental observations, so the model passes this
sanity check. Furthermore, the xanthosine and protein concentrations at the
upper fixed point have the expected order of magnitude: the xanthosine
concentration is roughly $10-100 \unit{nM}$, and there are roughly $500$
proteins, which is just a bit lower than what was measured for the number of
Nup transporters~\cite{Li2014} which fulfill a similar purpose. We do not
have well founded expectations for the other fixed points, so no comparison
can be made here. Nevertheless, the orders of magnitude at the lower fixed
point -- roughly $1-10 \unit{nM}$ of xanthosine and around $5$ proteins --
seem perfectly reasonable. Note that $\n{[x]_a} \approx \n{[c]_a}$ at the
lower fixed point because there is only weak accumulation due to Nup and a
few XapB transporters.

@@

As a remark we point out that we have not observed any oscillations in the
system. Intuitively, they might be expected when the XapA rate is
significantly larger than the XapB rate, but it turns out that oscillations
cannot be obtained. This can be understood when looking at the regions that
are bounded by all three nullclines: within these regions, the streamlines
on the nullclines point into the regions, so deterministically, the system
is trapped in there and can only flow towards the fixed points.

@@

\paragraph*{The extracellular xanthosine concentration.}
The parameter that is the experimentally most easily tunable and
biologically the most relevant is the extracellular xanthosine
concentration. When it is increased in the experiment, the cells go from all
being in the low expression state to being in either the low or the high
expression state (all-or-none phenomenon) to all being in the high
expression state~\cite{Chure2019}. If our model is correct, it should
exhibit the same qualitative behavior. Indeed we find exactly this: as can
be seen in Fig~\ref{fig5:extraxanth}, increasing $\n{[c]_a}$ makes the high
stable fixed point appear and then, for even higher $\n{[c]_a}$, the lower
one disappear. Thus, for low $\n{[c]_a}$ the only stable point of the system
is at low expression, and for high $\n{[c]_a}$ there is only high
expression. In between, there are two deterministically stable expression
levels.

@@

Furthermore, by setting $\n{[c]_a}=0$ (not shown here) we found that in the
absence of xanthosine, there are roughly 2-3 proteins, which agrees very
well with measurements, where around 2 proteins per cell were
found~\cite{Li2014}. In addition, the parameter $K_{\n{\chi A}}$
(dissociation constant of xanthosine from active XapR) can be tuned such
that the extracellular xanthosine concentration $\n{[c]_a}$ in the
switching-regime is similar to that in the experiment. It was found that the
cell only adapts at very high xanthosine concentrations of almost a
millimolar~\cite{Norholm2001} which is not completely unexpected when
recalling that for \emph{lac}, cells also limit themselves to glucose as
long as possible. Interestingly, because there is no parameter other than
$K_{\n{\chi A}}$ that tunes the critical value of $\n{[c]_a}$, this tells us
that $K_{\n{\chi A}}$ is large as argued in the estimation of $K_{\n{\chi
A}}$ in~\nameref{S1_Text}. Thus, the interaction between xanthosine and XapR
should be weak.

\paragraph*{The roles of XapA and XapB.}
While it is clear that the bistability in the model system is due to the
feedback loop from XapA and XapB, it is not obvious if both XapA and XapB
are necessary. It turns out that the bistability is due to XapB only. XapA
is neither sufficient nor necessary and, within the estimated parameter
regime, does not even have a significant influence on the system. This can
be seen from the plots in figure~\ref{fig6:xapAB}. XapA lowers the upper
solution by a little and could, in principle, thereby make the
high-expression solution vanish. For our choice of all other parameters,
this requires $k_{\n{\alpha}} > 10^4$ which is far from what has been
measured. However, a higher rate could, in principle, be achieved by
different translation rates of XapA and XapB (see simplifications of the
model in~\nameref{S1_Text}). Hence, we cannot exclude the possibility that
XapA gets so strong that it makes bistability impossible, but this is an
extreme case. XapB, on the other hand, is essential; without it the system
only has the one fixed point at low expression.

@@

For a cell, the above is a useful feature: by coupling XapA and XapB on an
operon, XapA is switched on and off together with XapB but it does not
significantly disturb this adaptation mechanism, while its kinetic
parameters can be chosen somewhat freely as necessary for metabolism. By
having a membrane transporter gene on an operon whose expression is
activated by the transporter substrate, the expression of a whole set of
enzymes can be turned on and off depending on the presence of the substrate.
It seems likely that this way of short-term adaptation of a single cell to
its environment may be used by cells for many metabolic processes.

\paragraph*{The role of cooperativity.} 
The model has two cooperatively interacting binding sites for XapR on the
\emph{xapAB} promoter and two cooperative binding sites on XapR for
xanthosine. An interesting question to pose is whether the cooperativity is
a necessary feature for bistability. This is motivated by the importance of
cooperativity in typical ``genetic switches''\cite{Gardner2000,Cherry2000}.

If, as a purely theoretical consideration, we remove either the second
xanthosine binding site on XapR or the second XapR binding site on the
promoter, we find that the system still has a bistable parameter regime.
However, this is only a rather narrow parameter range which makes the system
less stable. When the second binding site is removed in both places, the
equations are insufficiently non-linear to produce bistability. An example
of these three scenarios can be seen in Fig~\ref{fig7:coop}. It follows that
there need to be either two xanthosine binding sites on XapR or two XapR
binding sites on the promoter (or both) in order to obtain a switch-like
behavior.

@@

Note that we are not writing Hill equations and measuring cooperativity in
terms of the Hill coefficient. If Hill equations were to be used for the
modeling, the Hill coefficient could have values between 1 and 2, which
would yield bistability for large enough values, but not for lower ones.
This could be investigated more rigorously similar to the analysis of a
simple genetic switch in~\cite{Cherry2000}. However, we refrain from looking
for a minimal Hill coefficient in our system, because we do not find this
very insightful. Hill equations only describe scenarios with multiple,
non-interacting binding sites where any other state but the fully occupied
and active or the fully empty and inactive state is not significantly
populated. In that sense, the Hill coefficient simply denotes the number of
binding sites and does not reflect how cooperative these binding sites are.
We suggest that cooperativity should be explored more in-depth and a more
rigorous analysis of the role of cooperativity in simple genetic switches
should be done before returning to more complex systems like this one.

>>>>

\paragraph*{Xanthosine dynamics.}
Having described how xanthosine activates the synthesis of XapA and
XapB through XapR, we now close the feedback loop
by setting up a xanthosine rate equation.

\todo{MJM: Is this para \& next excessively detailed for main text?
maybe replace w/ 1-2 sentences about low affinity Mich-Ment transporters
that supplement XapB, \& shift all this to supplement?
If we want to emphasize the general class of model rather than the particular
biology details of Xap}
Transport of xanthosine across the cell membrane happens in two steps which
we will discuss now. All statements in this paragraph are based on data
from~\cite{Norholm2001}. In a first transport step, xanthosine passes the
outer membrane through porins like Tsx, OmpF and OmpC. This does not seem to
be a rate-limiting step. Then, XapB actively transports it across the inner
membrane, powered by the proton motive force. There are two other active
nucleoside transporters that seem to be transporting xanthosine with a very
low affinity: NupC and NupG. It was found that \textDelta\emph{nupC}
\textDelta\emph{nupG} strains cannot grow on xanthosine. Hence, these seem
to be necessary to ``start'' the system by importing small amounts of
xanthosine that then activate \emph{xapB}, and there appears to be no other
significant way in which xanthosine can enter the cell.

@@

After transport into the cell, XapA degrades xanthosine. We model this using
standard Michaelis-Menten kinetics, with parameters $k_{\n{a}}, K_{\n{a}}$
(corresponding to turnover rate and Michaelis constant, respectively). All
the above then leads to the xanthosine rate equation
\begin{eqnarray}
\dd{\n{[x]}}{t} = \biggl(\underbrace{k_{\n{b,i}} \frac{c}{K_{\n{b,i}} + c} - k_{\n{b,e}} \frac{\n{[x]}}{K_{\n{b,e}} + \n{[x]}}}_{\n{XapB}} - \underbrace{k_{\n{a}} \frac{\n{[x]}}{K_{\n{a}} + \n{[x]}}}_{\n{XapA}}\biggr) \n{[p]} + \underbrace{k_{\n{nup}} \left(c- \xi \n{[x]}\right)}_{\n{NupC\ \& \ NupG}}.
\end{eqnarray}
We recall that $\n{[x]}$ is the intracellular xanthosine concentration, while
$c$ denotes the extracellular. Because $k_{\n{b,i}} > k_{\n{b,e}}$ and
$K_{\n{b,i}} < K_{\n{b,e}}$, influx dominates at low intracellular
xanthosine concentrations. At much higher intra- than extracellular
xanthosine concentrations, the efflux term takes over. More details on the
aforementioned steps and a discussion of passive diffusion can be found
in~\nameref{S1_Text}.

@@

Very little is known about the \emph{xap} system, and thus, there are almost no
measured values for the free parameters. Nevertheless, we were able to
estimate a reasonable range by using values from similar, well studied
systems and by finding physical constraints or relations between parameters.
The results of these estimates are shown in Table~\ref{table1:nondim}. They
are based on a choice of $\gamma_{\n{p}} = 5 \cdot 10^{-4} \unit{s^{-1}}$
and $K_{\n{a}} = 5 \cdot 10^{-5} \unit{M}$. A detailed derivation can be
found in~\nameref{S1_Text}.

@@

\subsection*{Deterministic phase portraits}
A standard way to analyze dynamical systems deterministically is
to plot phase portraits. In the following, we present such plots where the
state variables are the mRNA, the protein, and the xanthosine concentration.

\paragraph*{From a 3D to a 2D system.} 
Fig~\subref{fig4:bistability}{A} shows the 3D phase portrait for a
representative set of parameters (shown in Table~\ref{table1:nondim}),
whose choice is explained below. The plot looks rather complicated at first
but can be understood intuitively. The three planes are the nullclines and
the gray lines point in the direction in which the dynamical system moves at
each point. The planes intersect in three points, which are the steady-state
solutions of the dynamical system. For this choice of parameters, the system
first flows towards the mRNA nullcline, then it moves along that plane to
the intersection with the protein nullcline, and lastly, it moves along that
intersection line to one of the three intersection points of all three
planes.

@@

It is important to point out that, for a different set of parameters, the
dynamics can be quite different. There are, for example, scenarios where the
xanthosine kinetics are roughly as fast as the mRNA kinetics and the
dynamics unfolds in two steps: first to the intersection of the mRNA and the
xanthosine nullcline, then along that line to the protein nullcline and
thereby to a fixed point.

A usual simplification with genetic circuits like this is to assume the mRNA
concentration to be at steady-state, i.e., to write $\dd{\n{[m]_a}}{\tau}=0$
and solve this for $\n{[m]_a}(\n{[p]_a},\n{[x]_a})$ to simplify the 3D to a
2D system. This restricts the dynamics to the green plane in our plot, which
is reasonable here because as explained above, the system first flows
towards that plane before either the protein or the xanthosine concentration
changes significantly. However, as already pointed out, this is different
for other parameter values, and thus, this assumption does not hold in general.
If the xanthosine dynamics are faster than the mRNA dynamics, the
system first flows towards the xanthosine nullcline. In that case, forcing
it onto the mRNA nullcline leads to significant changes in the dynamics.

@@

\paragraph*{Bistability.} 
From the 2D plot in Fig~\subref{fig4:bistability}{B}, it can clearly be seen
that for the chosen parameters, there are three steady-state solutions.
Because the 2D plane that we are in now is the mRNA nullcline, these
solutions are the same fixed points as in the 3D plot
($\dd{\n{[m]_a}}{\tau}=0$ on the nullcline and $\dd{\n{[p]_a}}{\tau}=0$,
$\dd{\n{[x]_a}}{\tau}=0$ for the 2D fixed points). One can see from the
vector field that the two outer points (labeled 1 and 3) are stable and the
middle one (labeled 2) is unstable and serves as a sort of ``switch-point''
between the other two. This means that there are two stable states the cell
can be in, one at high (point 3) and one at low (point 1) expression. As a
result, there is bistability and the distribution of expression among cells
can be bimodal, depending on initial conditions.

\todo{MJM: Do any of the older papers have data for this too,
or were they all just colony growth screens on plates?}
This corresponds to the experimental observations\cite{Chure2019}, so the model passes this
sanity check. Furthermore, the xanthosine and protein concentrations at the
upper fixed point have the expected order of magnitude: the xanthosine
concentration is roughly $10-100 \unit{mM}$, and there are roughly $500$
proteins, which is just a bit lower than what was measured for the number of
Nup transporters~\cite{Li2014} which fulfill a similar purpose. We do not
have well founded expectations for the other fixed points, so no comparison
can be made here. Nevertheless, the orders of magnitude at the lower fixed
point -- roughly $1-10 \unit{nM}$ of xanthosine and around $5$ proteins --
seem perfectly reasonable. Note that $\n{[x]_a} \approx \n{[c]_a}$ at the
lower fixed point because there is only weak accumulation due to Nup and a
few XapB transporters.

@@

As a remark we point out that we have not observed any oscillations in the
system. Intuitively, they might be expected when the XapA rate is
significantly larger than the XapB rate, but it turns out that oscillations
cannot be obtained. This can be understood when looking at the regions that
are bounded by all three nullclines: on these boundaries, the streamlines
point into the regions, so deterministically, they serve as
trapping regions from which the system cannot escape. Once inside, the only
possible trajectory is non-oscillatory flow towards the stable fixed point.

@@

\paragraph*{The extracellular xanthosine concentration.}
The parameter that is the experimentally most easily tunable and
biologically the most relevant is the extracellular xanthosine
concentration. When it is increased in experiments, the cells go from all
being in the low expression state to being in either the low or the high
expression state (all-or-none phenomenon) to all being in the high
expression state~\cite{Chure2019}. If our model is correct, it should
exhibit the same qualitative behavior. Indeed we find exactly this: as can
be seen in Fig~\ref{fig5:extraxanth}, increasing $\n{[c]_a}$ makes the high
stable fixed point appear and then, for even higher $\n{[c]_a}$, the lower
one disappear. Thus, for low $\n{[c]_a}$ the only stable point of the system
is at low expression, and for high $\n{[c]_a}$ there is only high
expression. In between, there are two deterministically stable expression
levels.

@@

Furthermore, we found that in the absence of xanthosine, i.e., setting
$\n{[c]_a}=0$ (not shown here), there are roughly 2-3 proteins, which agrees very
well with measurements, where around 2 proteins per cell were
found~\cite{Li2014}. In addition, the parameter $K_{\n{\chi A}}$
(dissociation constant of xanthosine from active XapR) can be tuned such
that the extracellular xanthosine concentration $\n{[c]_a}$ in the
switching-regime is similar to that in the experiment. It was found that the
cell only adapts at very high xanthosine concentrations of almost a
millimolar~\cite{Norholm2001} which is not completely unexpected when
recalling that for \emph{lac}, cells also limit themselves to glucose as
long as possible. Interestingly, because there is no parameter other than
$K_{\n{\chi A}}$ that tunes the critical value of $\n{[c]_a}$, this tells us
that $K_{\n{\chi A}}$ is large as argued in the estimation of $K_{\n{\chi
A}}$ in~\nameref{S1_Text}. Thus, we predict that the interaction between xanthosine and XapR
should be weak.

\paragraph*{The roles of XapA and XapB.}
While it is clear that the bistability in the model system is due to the
feedback loop from XapA and XapB, it is not obvious if both XapA and XapB
are necessary. It turns out that the bistability is due to XapB only. XapA
is neither sufficient nor necessary and, within the estimated parameter
regime, does not even have a significant influence on the system. This can
be seen from the plots in figure~\ref{fig6:xapAB}. XapA lowers the upper
solution by a small amount and could, in principle, thereby make the
high-expression solution vanish. For our choice of all other parameters,
this requires $k_{\n{\alpha}} > 10^4$ which is far from what has been
measured. However, a higher effective rate could, in principle, be achieved by
different translation rates of XapA and XapB (see simplifications of the
model in~\nameref{S1_Text}). Hence, we cannot exclude the possibility that
XapA becomes so strong that it makes bistability impossible, but this is an
extreme case. XapB, on the other hand, is essential; without it the system
only has the one fixed point at low expression.\footnote{
Seeger et.\ al.\cite{Seeger1995} observed that $\Delta xapB$ mutants could
survive, but grew extremely slowly, with xanthosine as the only carbon
source, which makes sense in light of Fig~\ref{fig6:xapAB}.
With \textit{xapB} removed, the switch never activates and the cells are
forced to survive with an extremely meager quantity of XapA to metabolize
the abundant xanthosine.}

@@

For a cell, the above is a useful feature: by coupling XapA and XapB on an
operon, XapA is switched on and off together with XapB but it does not
significantly disturb this adaptation mechanism, while its kinetic
parameters and expression levels can be chosen 
somewhat freely as necessary for metabolism. By
having a membrane transporter gene on an operon whose expression is
activated by the transporter substrate, the expression of a whole set of
enzymes can be turned on and off depending on the presence of the substrate.
It seems likely that this mechanism of short-term adaptation of a single cell to
its environment may be used by cells for many metabolic processes.

\paragraph*{The role of cooperativity.} 
The model has two cooperatively interacting binding sites for XapR on the
\emph{xapAB} promoter and two cooperative binding sites on XapR for
xanthosine. An interesting question to pose is whether the cooperativity is
a necessary feature for bistability. This is motivated by the importance of
cooperativity in ``typical'' genetic switches\cite{Gardner2000,Cherry2000}.

If, as a purely theoretical consideration, we remove either the second
xanthosine binding site on XapR or the second XapR binding site on the
promoter, we find that the system still has a bistable parameter regime.
However, this is only a rather narrow parameter range, which makes the system
\todo{MJM: the (hypothetical) utility of this switch seems to be resource efficiency,
which $\Rightarrow$ pushing the fixed points to extreme highs \& lows is good
$\Rightarrow$ stronger coop is good. maybe we should work this in}
less bistable. When the second binding site is removed in both places, the
equations are insufficiently non-linear to produce bistability. An example
of these three scenarios can be seen in Fig~\ref{fig7:coop}. It follows that
there need to be either two xanthosine binding sites on XapR or two XapR
binding sites on the promoter (or both) in order to obtain a switch-like
behavior.

@@

Note that we are not writing Hill equations and measuring cooperativity in
terms of the Hill coefficient. If Hill equations were to be used for the
modeling, the Hill coefficient could have values between 1 and 2, which
would yield bistability for large enough values, but not for lower ones.
This could be investigated more rigorously similar to the analysis of a
simple genetic switch in~\cite{Cherry2000}. However, we refrain from looking
for a minimal Hill coefficient in our system, because we do not find this
very insightful. Hill equations only describe scenarios with multiple,
\todo{MJM: but that already sounds like an effective interaction,
I'm not sure I like this phrasing, or the next sentence's.}
non-interacting binding sites where any other state but the fully occupied
and active or the fully empty and inactive state is not significantly
populated. In that sense, the Hill coefficient simply denotes the number of
binding sites and does not reflect how cooperative these binding sites are.
We suggest that cooperativity should be explored more in-depth and a more
rigorous analysis of the role of cooperativity in simple genetic switches
should be done before returning to more complex systems like this one.
